\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-31 OaklandSubmission/eval.tex

%dataset | time | comm | timeL | timeW | comm
%Our decision tree numbers in Table~\ref{tab:dt} further validate
%this claim. 
%We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
%describe specialized protocols for trees and forests (that perform
%better than~\cite{shafindss}).
%Similar to Bost et al.~\cite{shafindss}, they also remarks that these
%computations are infeasible with Yao-based 2PC.
%Again, we observe that
%the performance of \tool generated generic 2PC
%code is competitive with specialized protocols. 
The results for Na\"{i}ve Bayes are
in Table~\ref{tab:nb}. As before, $d$ denotes the length of the input
feature vector $x$ and $F$ is the number of possible values of $x_i$
for each $i \in [d]$.
%Although, there are no multiplications in these benchmarks, these do
%have a significant number of comparisons (due to array look-ups using
%secret indices) that
%result in many boolean-and gates. %(13k/750k denote 13000/75000). 
As before, we compare with Bost et al.~\cite{shafindss} and observe that \tool generated code
has better performance, despite using a generic 2PC,
as opposed to custom designed protocols developed by Bost et
al. Moreover, they remark that in their setup, generic Yao-based 2PC
did not scale to the smallest of their Na\"{i}ve Bayes classifiers, so
they had to scale down the prediction task, and even then Yao-based \mpc
was 500x slower. Whereas, we show that by using a
cryptographic-cost aware compiler, we can scale generic 2PC to real
prediction tasks, and get performance competitive to or better than the
specialized protocols. Table~\ref{tab:dt} 
compares against the more recent work of~\cite{wu}
on decision trees and further validates this claim.
\\\\
\noindent\textbf{Deep neural nets}
We evaluate \tool on the DNNs described in SecureML~\cite{secureml},
Cryptonets~\cite{cryptonets}, and the CNN from \minion~\cite{minionn}. For
comparison, we consider their implementations from
\minion~\cite{minionn}, which outperforms their previous
implementations. Table~\ref{tab:nn} shows the
results\footnote{\minion does not report the network round-trip time nor the bit-length of their inputs (we use $32$-bit inputs).}.
We note that for each of these DNNs, \minion provides a
specialized protocol, while \tool uses a generic 2PC protocol
(auto) generated from high-level code.

>>>>

%dataset | time | comm | timeL | timeW | comm
%Our decision tree numbers in Table~\ref{tab:dt} further validate
%this claim. 
%We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
%describe specialized protocols for trees and forests (that perform
%better than~\cite{shafindss}).
%Similar to Bost et al.~\cite{shafindss}, they also remarks that these
%computations are infeasible with Yao-based 2PC.
%Again, we observe that
%the performance of \tool generated generic 2PC
%code is competitive with specialized protocols. 
The results for Na\"{i}ve Bayes are
in Table~\ref{tab:nb}. As before, $d$ denotes the length of the input
feature vector $x$ and $F$ is the number of possible values of $x_i$
for each $i \in [d]$.
%Although, there are no multiplications in these benchmarks, these do
%have a significant number of comparisons (due to array look-ups using
%secret indices) that
%result in many boolean-and gates. %(13k/750k denote 13000/75000). 
As before, we compare with Bost et al.~\cite{shafindss} and observe that \tool generated code
has better performance, despite using a generic 2PC,
as opposed to custom designed protocols developed by Bost et
al. Moreover, they remark that in their setup, generic Yao-based 2PC
did not scale to the smallest of their Na\"{i}ve Bayes classifiers, so
they had to scale down the prediction task, and even then Yao-based \mpc
was 500x slower. Whereas, we show that by using a
cryptographic-cost aware compiler, we can scale generic 2PC to real
prediction tasks, and get performance competitive to or better than the
specialized protocols. Table~\ref{tab:dt} 
compares against the more recent work of~\cite{wu}
on decision trees and further validates this claim.
\\\\
\noindent\textbf{Deep neural nets.}
We evaluate \tool on the DNNs described in SecureML~\cite{secureml},
Cryptonets~\cite{cryptonets}, and the CNN from \minion~\cite{minionn}. For
comparison, we consider their implementations from
\minion~\cite{minionn}, which outperforms their previous
implementations. Table~\ref{tab:nn} shows the
results\footnote{\minion does not report the network round-trip time nor the bit-length of their inputs (we use $32$-bit inputs).}.
We note that for each of these DNNs, \minion provides a
specialized protocol, while \tool uses a generic 2PC protocol
(auto) generated from high-level code.

### 2017-10-31 OaklandSubmission/impl.tex
minor

\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. 
ABY provides a GMW-based~\cite{gmw} and a  Yao-based~\cite{yao} protocol for boolean computations.
Although \tool can generate code for both, we have observed better performance when using the latter
and use it in our evaluation.
We use the default ABY configuration for our
experiment \footnote{We set the security parameter to 128 and use OT
extension-based arithmetic multiplication triples generation.}. ABY
provides multi-threading support (for the offline phase of the \mpc
protocol); we leverage the support and use at most four threads in our
evaluation.

\tool programs can have the following operators:
addition, subtraction, multiplication, division by powers of two, left
shift,
logical and arithmetic right shifts, bitwise-(and, or, xor), unary
negation, 
bitwise-negation, logical-(not, and, or, xor), and comparisons (less
than, greater than, equality).  
Because of their high cost, integral division and floating-point
operators are not supported natively by \tool. 
However, we have implemented integral division in 30 lines of \tool,
while the floating-point support in ABY is under active
development~\cite{ddkssz15}.

@@

Our implementation assigns the type labels (rule~{\sc{T-Decl}})
conservatively. Only the variables that govern the control flow, i.e.,
variables in \kw{if}-conditions and \kw{for}-loop counters are
assigned public labels.
All other variables are assigned arithmetic labels (that can later be
coerced to boolean).
We leave a more sophisticates type inference procedure for future work.

>>>>

\section{Implementation}
\label{sec:impl}
We discuss some  implementation details of \tool.
The  \tool compiler is written in Python and
compiles each of our benchmarks in under a second to C++ code that
makes calls to the ABY
library~\cite{aby}. 
ABY provides a GMW-based~\cite{gmw} and a  Yao-based~\cite{yao} protocol for boolean computations.
Although \tool can generate code for both, we have observed better performance when using the latter
and use it in our evaluation.
We use the default ABY configuration for our
experiment\footnote{We set the security parameter to 128 and use OT
extension-based arithmetic multiplication triples generation.}. ABY
provides multi-threading support (for the offline phase of the \mpc
protocol); we leverage the support and use at most four threads in our
evaluation.

\tool programs can have the following operators:
addition, subtraction, multiplication, division by powers of two, left
shift,
logical and arithmetic right shifts, bitwise-(and, or, xor), unary
negation, 
bitwise-negation, logical-(not, and, or, xor), and comparisons (less
than, greater than, equality).  
Because of their high cost, integral division and floating-point
operators are not supported natively by \tool. 
However, we have implemented integral division in 20 lines of \tool,
while the floating-point support in ABY is under active
development~\cite{ddkssz15}.

@@

Our implementation assigns the type labels (rule~{\sc{T-Decl}})
conservatively. Only the variables that govern the control flow, i.e.,
variables in \kw{if}-conditions and \kw{for}-loop counters are
assigned public labels.
All other variables are assigned arithmetic labels (that can later be
coerced to boolean).
We leave a more sophisticated type inference procedure for future work.

### 2017-10-31 OaklandSubmission/intro.tex

 Today it is hard for the developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of cryptographic protocols, and therefore cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a general
 purpose, high-level programming language and a
 tool, e.g. a compiler, would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

 This paper presents such a framework for Secure
 Two-party Computation (\mpc),
%
%Most cryptographic tools rely on circuit as abstractions for any general computation but real-life developers write programs. It is critical to address this fundamental  representation gap to make cryptography accessible to non-crypto specialist developers. In this work, we address this gap for the case of secure multi-party computation.
%
%Most cryptographic tools are very hard to use non-crypto specialist developers. The task becomes even more tedious and error-prone for the case of secure multiparty computation since different protocol implementations require the function to be expressed in different representations such as Boolean or Arithmetic circuits. To make cryptography accessible to non-crypto specialist developers, we need to design systems that do crypto automatically and satisfy the properties of ... 
%
%Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is
a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a publicly known joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g. a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the classifier, beyond what is revelaed by the output
label.

%Since its introduction in 1980s, there has been a long
%sequence of work that has transformed 2PC from a mere theoretical tool to
%something practically efficient and usable.
%Our goal is to build a framework that enables programmers, who are not
%experts in cryptography, to easily program efficient and scalable \mpc
%protocols. 
To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Say Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server classifier, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w^{T}$ and $x$. Alice has following options.

@@

Alternatively, Alice can use a tool such as ABY (Demmlet et
al.~\cite{aby}) that allows
the computation to be expressed as a combination of arithmetic and
boolean circuits. However, here, the programming interface is quite
low-level -- the programmer is required to first manually split the
computation into arithmetic and boolean components, and then write the
circuits for all the components manually, including the appropriate
inter-conversion gates between them. Clearly, writing correct
and efficient protocols in such a framework is beyond an average
programmer who does not understand the various trade-offs between
arithmetic and boolean circuits, and even for an expert cryptographer,
writing large computations in such a framework can be tedious and
error-prone (a sentiment echoed by Demmler et al.~\cite{aby} themselves).

>>>>

 Today it is hard for the developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of cryptographic protocols, and therefore cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a, general
 purpose, high-level programming language and a
 tool, e.g., a compiler would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

 This paper presents such a framework for Secure
 Two-party Computation (\mpc),
%
%Most cryptographic tools rely on circuit as abstractions for any general computation but real-life developers write programs. It is critical to address this fundamental  representation gap to make cryptography accessible to non-crypto specialist developers. In this work, we address this gap for the case of secure multi-party computation.
%
%Most cryptographic tools are very hard to use non-crypto specialist developers. The task becomes even more tedious and error-prone for the case of secure multiparty computation since different protocol implementations require the function to be expressed in different representations such as Boolean or Arithmetic circuits. To make cryptography accessible to non-crypto specialist developers, we need to design systems that do crypto automatically and satisfy the properties of ... 
%
%Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is
a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a publicly known joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g., a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the classifier, beyond what is revelaed by the output
label.

%Since its introduction in 1980s, there has been a long
%sequence of work that has transformed 2PC from a mere theoretical tool to
%something practically efficient and usable.
%Our goal is to build a framework that enables programmers, who are not
%experts in cryptography, to easily program efficient and scalable \mpc
%protocols. 
To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Say Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server classifier, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w$ and $x$. Alice has following options.

@@

Alternatively, Alice can use a tool such as ABY (Demmlet et
al.~\cite{aby}) that allows
the computation to be expressed as a combination of arithmetic and
boolean circuits. However, here, the programming interface is quite
low-level: the programmer is required to first manually split the
computation into arithmetic and boolean components, and then write the
circuits for all the components manually, including the appropriate
inter-conversion gates between them. Clearly, writing correct
and efficient protocols in such a framework is beyond an average
programmer who does not understand the various trade-offs between
arithmetic and boolean circuits, and even for an expert cryptographer,
writing large computations in such a framework can be tedious and
error-prone (a sentiment echoed by Demmler et al.~\cite{aby} themselves).
